Supplement for: Carbon cycling in mature and regrowth forests globally

### 2021-03-01 manuscript/submissions/2021_03_01/response_to_reviews.Rmd

### Referee: 4

COMMENTS TO THE AUTHOR(S)
I am satisfied with the revised manuscript and feel it is now acceptable for publication.

I did find a couple of typos (e.g., L142: change "crated" to "created") and suggest the authors give the manuscript a once over.

**We fixed the noted typo and proofread the entire manuscript a few times.**

@@

COMMENTS TO THE AUTHOR(S)
I find the authors did a thorough and good job responding to concerns from the last round of review. I appreciate the re-organization of the introduction, and the changes made to the figures (including the inclusion of a conceptual figure). This is a nice paper. I have just two suggestions for minor amendments before final submission:

a) It'd be nice to return explicitly to the Odum hypotheses more clearly in the discussion. It seems that the results, as they are, do not support the prediction that NEP becomes near-zero in the most mature ecosystems (noting that Odum predicted this would happen in the southeastern US by 100 years of age). I think its important to highlight this fact explicitly (though possible some of this result is driven by CO2 fertilization effects).

**We have modified the paragraph in the discussion that discusses age trends in $NEP$ to refer back to the Odum hypothesis. It now reads as follows:**

**Notably, net carbon sequestration (NEP) exhibits an overall increase with age across the first 100 years of stand development, with more pronounced patterns in temperate than boreal forests (Fig. 7). This finding is consistent with previous studies showing an increase in NEP across relatively young stand ages (Baldocchi et al 2001, Pregitzer and Euskirchen 2004, Luyssaert et al 2008). However, NEP is theoretically expected to peak in intermediate-aged stands and thereafter decline, consistent with decelerating C accumulation as stands age (Fig. 9, Odum 1969), and such declines have been documented (Law et al 2003, Luyssaert et al 2008). The fact that NEP values estimated by our models for 100-year-old stands were not systematically different from those of mature stands (lower for temperate broadleaf, higher for temperate conifer, and equal for boreal; Fig. 9) may be driven by differences in geographical representation across age classes or by the fitting of an inappropriate functional form. Moreover, both biomass and non-living C stocks often continue to increase well beyond the 100-yr threshold used here to delimit young and mature stands (Luyssaert et al 2008, Lichstein et al 2009, McGarvey et al 2014). Additional data, including on age trends of deadwood, the organic layer, and soil C will be important to parsing the timing and extend of an age-related NEP decrease across forest biomes.**

### 2021-03-01 manuscript/ERL_global_C_review.Rmd
working on files for review

# KNIT IN FIGURES? 
generate_figures=TRUE
#note: table fails when knitting in word

@@

schematics_caption_generic ="Arrows indicate fluxes (Mg C ha$^{-1}$ yr$^{-1}$); boxes indicate stocks (Mg C ha$^{-1}$), with variables as defined in Table 1. Presented are mean ± std over geographically distinct areas (clusters of plots within 25 km of each other). Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. To illustrate the magnitude of different fluxes, arrow width is proportional to the square root of the corresponding flux. Mean component fluxes do not necessarily add up to the mean total fluxes because different sets of sites are included depending on data availability (Figs. S5-S30). Mature forests are defined  as $\\ge$ 100 years old and with no known major natural or anthropogenic disturbance in that time."
TrB_mature_caption = paste( "Figure 3 | C cycle diagram for mature tropical broadleaf forests. ", schematics_caption_generic)  
TeB_mature_caption = paste( "Figure 4 | C cycle diagram for mature temperate broadleaf forests. ", schematics_caption_generic)  
TeN_mature_caption = paste( "Figure 5 | C cycle diagram for mature temperate conifer forests. ", schematics_caption_generic, "The temperate conifer biome in particular is subject to high variability, with highest fluxes and stocks in the high-biomass forests of the US Pacific Northwest. An asterisk after a variable name indicates lack of C cycle closure.")  
BoN_mature_caption = paste( "Figure 6 | C cycle diagram for mature boreaal conifer forests. ", schematics_caption_generic)

>>>>

# KNIT IN FIGURES? 
generate_figures=FALSE
#note: table fails when knitting in word

@@

schematics_caption_generic ="Arrows indicate fluxes (Mg C ha$^{-1}$ yr$^{-1}$); boxes indicate stocks (Mg C ha$^{-1}$), with variables as defined in Table 1. Presented are mean ± std over geographically distinct areas (clusters of plots within 25 km of each other). Dashed shape outlines indicate variables with records from <7 distinct geographic areas, and dashed arrows indicate fluxes with no data. To illustrate the magnitude of different fluxes, arrow width is proportional to the square root of the corresponding flux. Mean component fluxes do not necessarily add up to the mean total fluxes because different sets of sites are included depending on data availability (Figs. S5-S30). Mature forests are defined  as $\\ge$ 100 years old and with no known major natural or anthropogenic disturbance in that time."
TrB_mature_caption = paste( "Figure 3 | C cycle diagram for mature tropical broadleaf forests. ", schematics_caption_generic)  
TeB_mature_caption = paste( "Figure 4 | C cycle diagram for mature temperate broadleaf forests. ", schematics_caption_generic)  
TeN_mature_caption = paste( "Figure 5 | C cycle diagram for mature temperate conifer forests. ", schematics_caption_generic, "The temperate conifer biome in particular is subject to high variability, with highest fluxes and stocks in the high-biomass forests of the US Pacific Northwest. An asterisk after a variable name indicates lack of C cycle closure.")  
BoN_mature_caption = paste( "Figure 6 | C cycle diagram for mature boreal conifer forests. ", schematics_caption_generic)
